\documentclass[a4paper,man,natbib,floatsintext,12pt]{apa7}

\usepackage[english]{babel} %character and hyphenation rules specific to the language you choose
%\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{tabularx} %great for APA-style Tables
\usepackage{siunitx} % Required for good table alignmen
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage[utf8]{inputenc}
\usepackage{textgreek} % for Greek letters in text
\usetikzlibrary{shapes,decorations,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 1 cm,semithick,
    latent/.style ={ellipse, draw, minimum width = 0.7 cm},
    observed/.style ={rectangle, draw},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped}
}
\newcommand{\sigFtest}[4]{\textit{F}(#1,#2) = #3, \textit{p}$<$#4}
\newcommand{\nonsigFtest}[3]{\textit{F}(#1,#2) = #3, \textit{p}$>$.05}


\title{Psychometric Validation of the Mandarin Version of the Duke Misophonia Questionnaire}
\shorttitle{Validation of the Mandarin DMQ}
\author{Abby Wang}
\affiliation{College of William \& Mary}
\journal{Journal of Affective Disorder}
\abstract{Misophonia is a condition characterized by strong emotional and physiological responses to specific trigger sounds. While extensively studied in Western populations, research on misophonia in Chinese populations remains limited, possibly due to the lack of assessment instruments. This study aimed to develop and validate a Mandarin version of the Duke Misophonia Questionnaire (DMQ) for use in China. A sample of 704 Mandarin-speaking participants completed the DMQ alongside other psychometric instruments assessing related constructs, including anxiety, depression, hyperacusis, and obsessive-compulsive symptoms. Item Response Theory (IRT) analysis confirmed a predominantly comparable structure between the Mandarin and English versions, though some subscales exhibited cross-cultural differences. Reliability analyses indicated strong internal consistency, and validity assessments demonstrated robust convergent and discriminant validity. Notably, affective and cognitive responses to misophonic triggers showed significant correlations with anxiety and depressive symptoms, highlighting potential shared mechanisms. These findings support the Mandarin DMQ as a reliable and valid tool for assessing misophonia in Chinese populations and provide insights into cultural influences on misophonia symptomatology. Future research should further explore the role of cultural norms in shaping symptom expression and coping strategies.}
\keywords{Misophonia; Psychometrics; China; Mandarin; Duke Misophonia Questionnaire}
\authornote{This research was funded by the Duke Kunshan University Signature Work Office and Academic Services. The authors extend their sincere gratitude to Dr. Zachary Rosenthal’s research team at the Duke Center for Misophonia and Emotion Regulation for their expert guidance in refining survey translations and selecting appropriate constructs. We are also deeply grateful to Chyi Ricketts and Jason Qiu for their meticulous back-translation work, which added to the linguistic and cultural accuracy of our survey materials. Additionally, we would like to acknowledge Zachary Williams from Vanderbilt University for his insightful feedback on data interpretation. The authors confirm that no generative artificial intelligence tools were used in the drafting of this manuscript, including its text, figures, or any other content.}
\leftheader{Alternate page header in man mode}

%-------------- END PREAMBLE  -------------------


\begin{document}

\maketitle  %Insert my APA style title page

\input{intro.tex}

\input{method.tex}

\input{results.tex}

\input{discussion.tex}


\bibliography{references.bib}

\end{document}
https://www.overleaf.com/project/64ef8e5b3faa92d4248ddcf9